---
title: "group20"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{group20}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(group20)
```

### Function 1

### Function 2

### Function 3

### Function 4

I have made a function that takes a vector the output of previous function of codons and returns a string consisting of Amino acid abbriviations

### Function 5

Function 5 takes a string of amino acids (as letter abbreviation) and turns it into a bar chart which shows the number of occurrences of each amino acid. 

The function takes the string of amino acids and makes a vector. In this part, the str_split function from the "stringr"-package is applied. 

Afterwards, the function counts the number of occurences of each amino acids. It makes a new data frame (called "counts") of the amino acid-vector plus the new vector of counts which is saved as the column called "Counts".

This "counts"-data frame is used to make a ggplot (from the "ggplot2"-package). The function output is a bar chart with the amino acid letter abbreviation on the x-axis and the number of occurrences ("Counts") on the y-axis.
